Age-related changes in plant growth and traits

### 2015-05-27 results_RAschedules_shorter.Rmd
looking more at growth variables learning about PCA in R

>>>>

###Plotting RA species means against various traits
* species with higher wood density have higher RA
* taller species have lower RA
* species with higher LMA have lower RA
* no relationship between RA and seed size
* these are mean RA values across all plants, including babies and other non-reproducing individuals
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
mod <- lm(WD_mean~asin(sqrt(RA_mean)),SummarySpp)
words.bottom.left.logy(mod)
plot(RA_mean~seed_size, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(RA_mean)), SummarySpp)
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
plot(RA_mean~LMA_mean, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(LMA_mean)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
words.top.right.logxy(mod)
plot(RA_mean~maxH_spp, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(maxH_spp)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
words.bottom.left.logxy(mod)
mtext("RA",2,outer=TRUE)
```

*just plotting mean RA of mature plants is similar, although BAER throws off many plots - surprised by how high its RA is, and wondering if something is wrong with these #s
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(maxH_spp~WD_mean,data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logy(mod)
plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(LMA_mean)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.top.right.logxy(mod)
plot(mature_RA_mean~maxH_spp, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
mod <- lm(log(maxH_spp)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logxy(mod)
mtext("RA (mature plants only)",2,outer=TRUE)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
mod <- lm(log(growth_stem_diam) ~ age*WD_mean*LMA_mean*maxH_spp*RA, SummaryInd)
anova(mod)

spp_zero_RA <- SummaryInd %>%
  filter(RA==0) %>%
  group_by(species) %>%
  summarise_each(funs(length),RA)
spp_zero_RA$RAcex <- (((spp_zero_RA$RA)/20))

sppage_zero_RA <- SummaryInd %>%
  filter(RA==0) %>%
  group_by(species,age) %>%
  summarise_each(funs(length),RA)
sppage_zero_RA$RAcex <- (((sppage_zero_RA$RA)/10))

par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp[as.factor(species)],pch=16,log="y",ylim=c(.0008,1))
points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(WD_mean~asin(sqrt(RA)),SummaryInd)
words.bottom.left.logy(mod)
plot(RA~seed_size, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(seed_size)~asin(sqrt(RA)), SummaryInd)
words.bottom.left.logxy(mod)
plot(RA~LMA_mean, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=sppage_zero_RA$RAcex)
mod <- lm(log(LMA_mean)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.top.right.logxy(mod)
plot(RA~maxH_spp, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~maxH_spp,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(maxH_spp)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.bottom.left.logxy(mod)
```

### 2015-05-27 results_growth.Rmd
looking more at growth variables learning about PCA in R

>>>>

###Traits correlated
- species maxH and wood density are highly correlated
- the two species lying a bit outside are PUTU and PHPH which both often have multiple stems from the base - the second chart omits them
-
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
plot(WD_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
mod <- lm(log(maxH_spp)~WD_mean,SummaryInd)
words.bottom.left.logx(mod)

plot(WD_mean~maxH_spp,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
mod <- lm(log(maxH_spp)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
words.bottom.left.logx(mod)

plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
mod <- lm(log(total_weight_mean) ~ (seedset_mean),SummarySpp)
words.bottom.left.logx(mod)

plot(seedset_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
mod <- lm(log(maxH_spp) ~ (seedset_mean),SummarySpp)
words.bottom.left.logx(mod)
